RNA-seq from 4 cell populations

### 2021-07-28 deconvolution/fans4/molec_profiling.Rmd
bug fix

hush=function(code){
  sink("NUL") # use /dev/null in UNIX
  tmp = code
  sink()
  return(tmp)
}

@@

```{r predict.celltype}
df_class = lapply(1:10, function(k){

@@

### Esimate precision weights
```{r voom}
form = ~ (1|CellType) + (1|Individual.ID) + (1|Gender)
vobj = voomWithDreamWeights(dge, form, info, plot=TRUE, save.plot=TRUE, BPPARAM=SnowParam(36, progressbar=TRUE))
```

>>>>

@@

```{r predict.celltype}

X = as.matrix(df_pca[,2:200])

@@

### Esimate precision weights
```{r voom}
form = ~ (1|CellType) + (1|Individual.ID) + (1|Gender) + (1|Batch)
vobj = voomWithDreamWeights(dge, form, info, plot=TRUE, save.plot=TRUE, BPPARAM=SnowParam(36, progressbar=TRUE))
```
